% !TEX root = ../main.tex
\addchap{Abstract}\label{Abstract}
\begin{refsection}

This book investigates the associations between \isi{information structure}
and linguistic forms in spoken Japanese
mainly by analyzing spoken corpora.
It proposes multi-dimensional annotation and analysis procedures of spoken corpora and
explores the relationships between \isi{information structure}
and particles, \isi{word order}, and intonation.

Particles, \isi{word order}, and intonation in spoken Japanese have been investigated separately in different frameworks and different subfields in the literature;
there was no unified theory to account for the whole phenomena.
This book investigated the phenomena as a whole in a consistent way
by annotating all target expressions according to the same criteria and
by employing the same analytical framework.
Chapter \ref{Introduction} outlines the questions to be investigated and introduces the methodology of this book.
Chapter \ref{Background} reviews the literature of Japanese linguistics
as well as the literature on \isi{information structure} in different languages.
Chapter \ref{Framework} proposes the analytical framework of the book.
Major findings are discussed in Chapter \ref{Particles}, \ref{WordOrder}, and \ref{Intonation}.

Chapter \ref{Particles} analyzes the distributions of \isi{topic} and case particles.
It is made clear that so-called \isi{topic} particles 
(\ci{wa}, the zero particles, \ci{toiuno-wa}, and \ci{kedo/ga} preceded by \isi{copula}) are mainly sensitive to the given-new taxonomy,
whereas case particles (\ci{ga}, \ci{o}, and the zero particles) are sensitive to both focushood and grammatical function.
While the distinction between \ci{wa} and \ci{ga} attract much attention in traditional Japanese linguistics,
the distribution of different kinds of \isi{topic} and case particles, including the zero particles,
are analyzed in this book.

Chapter \ref{WordOrder} studies \isi{word order}:
i.e., clause-initial, pre-predicate, and post-pred\-i\-cate noun phrases.%
%%%ISSUE OUT OF ALIGNMENT
Topical NPs appear either clause-initially or post-pred\-i\-cat\-ively,
while focal NPs appear pre-predicatively.
Clause-initial and post-predicate NPs are different mainly in statuses in the given-new taxonomy.
The previous literature investigated clause-initial, pre-predicate, and post-predicate constructions in different frameworks;
however, there was no unified account for \isi{word order} in Japanese.
The book outlines \isi{word order} in spoken Japanese in a unified framework.

\newpage 
Chapter \ref{Intonation} investigates intonation.
While the previous literature mainly concentrates on \isi{contrastive focus},
this book discusses in terms of both \isi{topic} and focus.
It turns out that intonation corresponds to a unit of processing and
argues that \isi{information structure} influences the form of intonation units.

Chapter \ref{Discussion} discusses theoretical implications of these findings.
Finally, Chapter \ref{Conclusion} summarizes the book
and points out some remaining issues and possible future studies.

\end{refsection}
